\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[scale=0.75]{geometry}
\usepackage{hyperref}

\signature{David (Jiachen) Weng}
\address{David (Jiachen) Weng \\ thedavidweng@gmail.com \\ \href{https://thedavidweng.github.io}{thedavidweng.github.io} \\ Vancouver, BC, Canada}

\begin{document}

\begin{letter}{Hiring Committee \\ University of British Columbia \\ First Year \& Interdisciplinary Programs \\ Faculty of Arts}

\opening{Dear Hiring Committee,}

As a UBC Bachelor of Media Studies graduate with three professional roles across the university, including student housing, the Faculty of Medicine, and the Beaty Biodiversity Museum, and who through the Media Studies Student Association worked closely with BMS faculty, I have a firsthand understanding of how UBC's departments, communities, and partners connect. I'm excited to bring that insider perspective to the Community Engagement Coordinator role.

My experience maps closely to this position's core demands. As a Resident Advisor at UBC Student Housing, I designed and executed 12+ co-curricular programs annually, managed safety protocols, and facilitated cross-cultural events that engaged diverse populations. As an Educational Technology Assistant in UBC's Department of Physical Therapy, I collaborated with faculty to develop inclusive e-learning modules serving 200+ students, directly mirroring the CEL curriculum development and educational resource design this role requires. I'm comfortable working across departments, coordinating with campus services and external partners, and translating program goals into tangible student experiences.

Beyond programming, I bring the communications and budget skills this role demands. I managed financial operations as Treasurer of the Media Studies Student Association, handling grant applications, expense tracking, and compliance reporting. On the content side, I currently manage multi-platform publishing for the BC + AI Ecosystem and have produced visual assets, newsletters, and event communications, skills directly applicable to CEL marketing, website content, and outreach strategies.

The posting emphasizes cross-cultural sensitivity and the ability to work with a wide range of partners. As a bilingual English and Mandarin speaker who has built programming for culturally diverse communities, I bring both the interpersonal skills and the lived experience to foster genuine community partnerships. I would welcome the chance to discuss how my BMS background and operational experience could contribute to the program's CEL mandate.

\closing{Sincerely,}

\end{letter}
\end{document}
